### 2014-09-29 tex/definitions.tex
Rewrite some of mutual exclusion

\begin{definition}
A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relates machine states with successor states. Two important state transition relations are the \textbf{lazy state transition relation} $\rightarrow_\ell$ and the \textbf{summary state transition relation} $\rightarrow_s$.
\end{definition}

%\begin{definition}
%A \textbf{state sequence} is a sequence of states denoted as $\Pi_n = s_0,s_1,...,s_n$. A \textbf{feasible state sequence}, $\Pi_n^\phi = s_0,s_1,...,s_n$ is consistent with the transition: $\forall i\ (0 \leq i < n \Rightarrow s_i \rightarrow_{\Phi} s_{i+1})$, where $s_0\in \mathcal{S}_0$.
%\end{definition}
%
%%For 
%\begin{comment}
%\begin{definition}
%A \textbf{feasible state sequence} is defined as a sequence of states resulting from repeated application of the state transition relation to some initial state $s_0\in \mathcal{S}_0$: $$\Pi_n = s_0,s_1,...,s_n$$ where the relation $s_i \rightarrow_{\Phi} s_{i+1}$ holds for all $i \in \{ i | 0 \leq i < n \}$
%\end{definition}
%\end{comment}

@@

\begin{definition}
Given a sequence of states $$\Pi_n = s_0,s_1,...,s_n$$ where $$s_i = ( \mu_i\ \cfgnt{L}_i\ \cfgnt{R}_i\ \phi_i\ \eta_i\ \cfgnt{e}_i\ \cfgnt{k}_i )$$ the \textbf{control flow sequence} of $\Pi_n$ is the defined as the sequence of tuples $$ \pi_n = \mathbb{CF}(\Pi_n) = (\eta_0\ \cfgnt{e}_0\ \cfgnt{k}_0),(\eta_1\ \cfgnt{e}_1\ \cfgnt{k}_1),...,(\eta_n\ \cfgnt{e}_n\ \cfgnt{k}_n)$$
\end{definition}

@@

\begin{definition}
\label{def:homomorphism}
A \textbf{homomorphism} $s_x \rightharpoonup_{h} s_y$, from state $s_x = ( \cfgnt{L}_x\ \cfgnt{R}_x\ \phi_x\ \eta_x\ \cfgnt{e}_x\ \cfgnt{k}_x )$ to state $s_y = ( \cfgnt{L}_y\ \cfgnt{R}_y\ \phi_y\ \eta_y\ \cfgnt{e}_y\ \cfgnt{k}_y )$, is defined as follows: 
$$
\begin{array}{l}
 s_x \rightharpoonup_{h} s_y \Leftrightarrow \\
\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha \in \mathcal{L}\ (\forall \cfgnt{l}_\beta \in \mathcal{L}\ ( \forall f \in \mathcal{F}( \exists \phi_\alpha \in \Phi(\exists \phi_\beta \in \Phi( \\ 
\ \ \ \ \ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_x(\cfgnt{R}_x (\cfgnt{l}_\beta,f )) \Rightarrow (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_y(\cfgnt{R}_y (h(\cfgnt{l}_\beta),f ))\ \\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) ) ) )
\end{array}
$$
\end{definition}

>>>>

\begin{definition}
A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relat
es machine states with successor states. Two important state transition relations are the \textbf{lazy state transition relation} $\rightarrow_\ell$ and the \textbf{summary state transition relation} $\rightarrow_\varsigma$. Each of these use a separate relation for initialization: $\rightarrow_I$ for initialization the lazy transition relation and $\rightarrow_S$ for initialization the summary transition relation. All of these transition relations are defined in \figref{fig:lazy}, \figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
\end{definition}

\begin{definition}
A state $s = (\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k})$ is a \textbf{lazy state} if and only if $\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (|\cfgnt{L}(\cfgnt{r})| = 1)$]
\end{definition}

\begin{definition}
A state $s = (\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k})$ is a \textbf{summary state} if and only if 
$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (|\cfgnt{L}(\cfgnt{r})| \ge 1)$.
A lazy state is also a summary state by definition.
\end{definition}

\begin{definition}
A heap, $(\cfgnt{L}\ \cfgnt{R})$, is \textbf{location mutual exclusive} if and only if 
\[
\begin{array}{l}
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi_\alpha\ \cfgnt{l}_\alpha),(\phi_\beta\ \cfgnt{l}_\beta) \in \cfgnt{L}{r}\ (\\
\ \ \ \ \cfgnt{l}_\alpha \neq \cfgnt{l}_\beta \Rightarrow \phi_\alpha \wedge \phi_\beta = \cfgt{false}))
\end{array}
\]
\end{definition}
%\begin{definition}
%A \textbf{state sequence} is a sequence of states denoted as $\Pi_n = s_0,s_1,...,s_n$. A \textbf{feasible state sequence}, $\Pi_n^\phi = s_0,s_1,...,s_n$ is consistent with the transition: $\forall i\ (0 \leq i < n \Rightarrow s_i \rightarrow_{\Phi} s_{i+1})$, where $s_0\in \mathcal{S}_0$.
%\end{definition}
%
%%For 
%\begin{comment}
%\begin{definition}
%A \textbf{feasible state sequence} is defined as a sequence of states resulting from repeated application of the state transition relation to some initial state $s_0\in \mathcal{S}_0$: $$\Pi_n = s_0,s_1,...,s_n$$ where the relation $s_i \rightarrow_{\Phi} s_{i+1}$ holds for all $i \in \{ i | 0 \leq i < n \}$
%\end{definition}
%\end{comment}

@@

\begin{definition}
Given a sequence of states $$\Pi_n = s_0,s_1,...,s_n$$ where $$s_i = (\cfgnt{L}_i\ \cfgnt{R}_i\ \phi_i\ \eta_i\ \cfgnt{e}_i\ \cfgnt{k}_i )$$ the \textbf{control flow sequence} of $\Pi_n$ is the defined as the sequence of tuples $$ \pi_n = \mathbb{CF}(\Pi_n) = (\eta_0\ \cfgnt{e}_0\ \cfgnt{k}_0),(\eta_1\ \cfgnt{e}_1\ \cfgnt{k}_1),...,(\eta_n\ \cfgnt{e}_n\ \cfgnt{k}_n)$$
\end{definition}

@@

\begin{definition}
\label{def:homomorphism}
A \textbf{homomorphism} $s_x \rightharpoonup_{h} s_y$, from state $s_x = ( \cfgnt{L}_x\ \cfgnt{R}_x\ \phi_x\ \eta_x\ \cfgnt{e}_x\ \cfgnt{k}_x )$ to state $s_y = ( \cfgnt{L}_y\ \cfgnt{R}_y\ \phi_y\ \eta_y\ \cfgnt{e}_y\ \cfgnt{k}_y )$, is defined as follows: 
$$
\begin{array}{l}
 s_x \rightharpoonup_{h} s_y \Leftrightarrow \\
\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}( \exists \phi_\alpha\ (\exists \phi_\beta\ ( \\ 
\ \ \ \ \ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_x(\cfgnt{R}_x (\cfgnt{l}_\beta,f )) \Rightarrow (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_y(\cfgnt{R}_y (h(\cfgnt{l}_\beta),f ))\ \\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) ) ) )
\end{array}
$$
\begin{comment}
$$
\begin{array}{l}
s_x \rightharpoonup_{h} s_y \Leftrightarrow \\
\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathit{fields}(\mathrm{type}(\cfgnt{l}_\beta))\ ( \\
\ \ \ \ \ \ \ \ \ \ \ \ \forall (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_x(\cfgnt{R}_x (\cfgnt{l}_\beta,f ))\ ( \\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \exists \phi_\beta\ ((\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_y(\cfgnt{R}_y (h(\cfgnt{l}_\beta),f )))))))\\
\end{array}
$$
\end{comment}
\end{definition}

### 2014-09-29 tex/proofs.tex
Rewrite some of mutual exclusion

\subsection{Theorems}
%\begin{lemma}
%\label{lem:lazyrefprops}
%For any lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$, for any reference $r \in \cfgnt{L}_\ell^\leftarrow$, 
%$$ | \cfgnt{L}_\ell ( r) | = 1 $$
%\end{lemma}
%
%\begin{proof}
%In every rule in the Lazy machine that establishes a reference mapping, the value set contains exactly one location, constraint pair. 
%\end{proof}

\begin{theorem}[Mutual Exclusion]
\label{thm:mutex}
If we have a reachable summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, and any two pairs $(\phi_\alpha\ l_\alpha) \in \cfgnt{L}_s(r)$ and $(\phi_\beta\ l_\beta) \in \cfgnt{L}_s(r)$ such that $l_\alpha \ne l_\beta$, then
$$(\phi_\alpha \wedge \phi_\beta) = \cfgt{false}$$
\end{theorem}
\begin{proof}
The proof will proceed inductively.

@@

We begin by considering the Field Access rule. Suppose $s_s$ has the form $\lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$. In this case, the relationship between $s_s$ and $s_s^\prime$ is described by the Field Access rule. The Field Access rule uses the Summarize rule to describe the relation between $\cfgnt{L}_{s}$ and $\cfgnt{L}_{s^\prime}$. Because the summarize rule is essentially a fixed-point computation, we can reason about it as a machine that produces a sequence of intermediate states $s_1, s_2, ... , s_n$. We will use an inductive argument to show that the mutual exclusion property holds for any of those intermediate states. First, let state $s_\alpha$ be any state for which the property in Theorem~\ref{thm:mutex} holds, and let $s_\beta$ be the intermediate state where $s_\alpha \rightarrow_S s_\beta$. If all fields are initialized, then $s_\alpha$ and $s_\beta$ are identical, so the mutually exclusive property holds for $s_\beta$. 
Otherwise, there must be some location $\cfgnt{l}_{un} \in \cfgnt{L}_\alpha(r)$ for which field f contains a reference $r_a$ that could feasibly point to the uninitialized location. In this case, a new reference is created and a single entry is added to $\cfgnt{L}_\beta$. The elements of the set $\theta_{all} = \cfgnt{L}_\beta(\cfgnt{R}_\beta(\cfgnt{l}_{un},\cfgnt{f}))$ can be divided into four distinct subsets, $\theta_{cur}$, $\theta_{null}$, $\theta_{new}$, and $\theta_{alias}$. The set $\theta_{cur}$ contains the pairs containing locations from the reference $r_a$, $\theta_{null}$ contains the pair with the null location, $\theta_{new}$ contains a pair with a new location, and $\theta_{alias}$ contains pairs representing alias locations. Any two constraints in $\theta_{cur}$ are guaranteed to be pairwise mutually exclusive because of the inductive hypothesis, and any single constraint is guaranteed to be pairwise mutually exclusive with any constraint in $\theta_{null}$, $\theta_{new}$, or $\theta_{alias}$ because constraints in $\theta_{cur}$ contain the conjunct $\neg \phi$, while constraints in the other three sets are conjoined with $\phi$. The set $\theta_{null}$ contains only one element, which in turn contains the constraint $r_f = r_{null}$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{new}$, or $\theta_{alias}$ because constraints in those sets contain the conjunct $r_f \neq r_{null}$. The set $\theta_{new}$ contains one element, which in turn contains the constraint containing the conjunct $ \wedge_{\lp \cfgnt{r}^\prime_a,\ \phi^\prime_a,\ l^\prime_a\rp  \in \rho} \cfgnt{r}_f \ne \cfgnt{r}^\prime_a$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{alias}$, because each constraint in that set contains the conjunct $r_f = r_a$ for some $(r_a\ \phi_a\ l_a)\in \rho$. Any two elements of the set $\theta_{alias}$ are guaranteed to pairwise mutually exclusive because for each constraint that contains the conjunct $r_f = r_a$, every other constraint contains the conjunct $r_f \ne r_a$. Thus, all constraints from all pairs in $\theta{all}$ are guaranteed to be mutually exclusive, and the property from Theorem~\ref{thm:mutex} holds for intermediate state $s_\beta$.

We have now shown that whether there are any uninitialized fields or not, the mutual exclusivity property holds for any intermediate state $s_\beta$, so long as $s_\alpha \rightarrow_S s_\beta$ and the property holds for $s_\alpha$. 
So, since the mutual exclusivity property holds for $s_s$, $s_s \rightarrow_S s_1$, and $s_{i} \rightarrow_S s_{i+1} $ for all $i$ such that $0 < i < n$, we are guaranteed that the mutually exclusive property holds for the final intermediate state $s_n$. This concludes the inductive argument about intermediate state.

>>>>

\subsection{Theorems}
\begin{lemma}[Location Mutual Exclusion in $\rightarrow^*_S$]
Given a location mutual exclusive heap, $(\cfgnt{L}_0\ \cfgnt{R}_0)$, from a
summary state with a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the
new heap, $(\cfgnt{L}^\prime\ \cfgnt{R}^\prime)$, from the summary
initialization machine, $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
\rightarrow^*_S
(\cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}\ \cfgnt{f})$, after any number of machine steps, is also
location mutual exclusive.
\end{lemma}
\begin{proof}
Induction over the number of machine steps on the summary initialization machine in \figref{fig:symInit}.

\noindent\textbf{Base Case}. The machine takes one step: $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
\rightarrow_S
(\cfgnt{L}_1 \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f})$. Let $\Lambda = \mathbb{UN}(\cfgnt{L}_0, \cfgnt{R}_0, \cfgnt{r},
\cfgnt{f})$ be the set of uninitialized locations. If $\Lambda = \emptyset$, then the \texttt{Summarize (end)}
rule is active and $(\cfgnt{L}_1\ \cfgnt{R}_1) = (\cfgnt{L}_0\ \cfgnt{R}_0)$, which is location mutual exclusive by definition.

If $\Lambda \neq \emptyset$, then the \texttt{Summarize} rule is
active, and each new constraint location pair must be considered
individually. These pairs are partitioned into the sets
$\theta_\mathit{null}$, $\theta_\mathit{new}$,
$\theta_\mathit{alias}$, and $\theta_\mathit{orig}$ by the rule. 
\begin{itemize}
\item Any member of $\theta_\mathit{null}$, $\theta_\mathit{new}$, and
  $\theta_\mathit{alias}$ has a constraint of the form $\phi_x \wedge
  \ldots$ while any member of $\theta_\mathrm{orig}$ has a constraint
  of the form $\neg \phi_x \wedge \ldots$. As every
  $(\phi_\mathit{orig}\ \cfgnt{l}_\mathit{orig}) \in
  \cfgnt{L}_n(\cfgnt{R}_n(\cfgnt{l}_x,\cfgnt{f}))$ is location mutual exclusive
  by definition, members of $\theta_\mathit{orig}$ are location
  mutual exclusive with each other and with members in $\theta_\mathit{null}$,
  $\theta_\mathit{new}$, and $\theta_\mathit{alias}$.
\item Any member of $\theta_\mathit{null}$ has the form $\ldots \wedge
  \cfgnt{r}_f = \cfgnt{r}_\mathit{null}$ while any member of
  $\theta_\mathit{new}$ and $\theta_\mathit{alias}$ has the form
  $\ldots \wedge \cfgnt{r}_f \neq \cfgnt{r}_\mathit{null} \wedge
  \ldots$. As $\theta_\mathit{null}$ is a singleton set, its location is
  location mutual exclusive from those in $\theta_\mathit{new}$ and
  $\theta_\mathit{alias}$.
\item Any member of $\theta_\mathit{new}$ has a constraint of the form
  $\ldots \wedge ( \wedge_{(
  \cfgnt{r}_a,\ \phi_a,\ l_a) \in \rho}
  \cfgnt{r}_f \ne \cfgnt{r}_a) )$ to assert it does not
  alias anything while any member of $\theta_\mathit{alias}$ has
  the form $\ldots \wedge \cfgnt{r}_f = \cfgnt{r}_a \wedge \ldots$ for
  some alias $\cfgnt{r}_a$ with both partitions reasoning over the same set of aliases $\rho$.  As $\theta_\mathit{new}$ is a singleton set, its
  location is location mutual exclusive from any member of
  $\theta_\mathit{alias}$.
\item Any member of $\theta_\mathit{alias}$ has the form
\[\ldots \wedge \cfgnt{r}_f = \cfgnt{r}_a \wedge ( \wedge_{( \cfgnt{r}^{\prime}_a\ \phi^{\prime}_a\ l^{\prime}_a)  \in \rho\ ( \cfgnt{r}^\prime_a \neq \cfgnt{r}_a) } \cfgnt{r}_f \neq \cfgnt{r}^{\prime}_a)\]
Each is mutually exclusive over the particular alias it asserts.
\end{itemize}
Every member in $\theta = \theta_\mathit{null} \cup
\theta_\mathit{new} \cup \theta_\mathit{alias} \cup
\theta_\mathit{orig}$ is thus location mutual exclusive making $(\cfgnt{L}_1 \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f})$ location mutual exclusive as well.

\noindent\textbf{Inductive Step}. The machine takes $n$-steps:
\[
(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f}) \rightarrow_S (\cfgnt{L}_1\ \cfgnt{R}_1\ \cfgnt{r}\ \cfgnt{f}) \rightarrow_S \ldots \rightarrow_S
(\cfgnt{L}_n\ \cfgnt{R}_n\ \cfgnt{r}\ \cfgnt{f})
\]
By the induction hypothesis, $(\cfgnt{L}_n\ \cfgnt{R}_n)$ is location
mutual exclusive. This matches the base case, in that the heap on the
left side of the transition is location mutual exclusive, and by the
same argument as in the base case,
$(\cfgnt{L}_{n+1}\ \cfgnt{R}_{n+1})$ is thus location mutual exclusive.
\begin{comment}
The Field Access rule uses the Summarize rule to describe the relation between $\cfgnt{L}_{s}$ and $\cfgnt{L}_{s^\prime}$. Because the summarize rule is essentially a fixed-point computation, we can reason about it as a machine that produces a sequence of intermediate states $s_1, s_2, ... , s_n$. We will use an inductive argument to show that the mutual exclusion property holds for any of those intermediate states. First, let state $s_\alpha$ be any state for which the property in Theorem~\ref{thm:mutex} holds, and let $s_\beta$ be the intermediate state where $s_\alpha \rightarrow_S s_\beta$. If all fields are initialized, then $s_\alpha$ and $s_\beta$ are identical, so the mutually exclusive property holds for $s_\beta$. 
Otherwise, there must be some location $\cfgnt{l}_{un} \in \cfgnt{L}_\alpha(r)$ for which field f contains a reference $r_a$ that could feasibly point to the uninitialized location. In this case, a new reference is created and a single entry is added to $\cfgnt{L}_\beta$. The elements of the set $\theta_{all} = \cfgnt{L}_\beta(\cfgnt{R}_\beta(\cfgnt{l}_{un},\cfgnt{f}))$ can be divided into four distinct subsets, $\theta_{cur}$, $\theta_{null}$, $\theta_{new}$, and $\theta_{alias}$. The set $\theta_{cur}$ contains the pairs containing locations from the reference $r_a$, $\theta_{null}$ contains the pair with the null location, $\theta_{new}$ contains a pair with a new location, and $\theta_{alias}$ contains pairs representing alias locations. Any two constraints in $\theta_{cur}$ are guaranteed to be pairwise mutually exclusive because of the inductive hypothesis, and any single constraint is guaranteed to be pairwise mutually exclusive with any constraint in $\theta_{null}$, $\theta_{new}$, or $\theta_{alias}$ because constraints in $\theta_{cur}$ contain the conjunct $\neg \phi$, while constraints in the other three sets are conjoined with $\phi$. The set $\theta_{null}$ contains only one element, which in turn contains the constraint $r_f = r_{null}$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{new}$, or $\theta_{alias}$ because constraints in those sets contain the conjunct $r_f \neq r_{null}$. The set $\theta_{new}$ contains one element, which in turn contains the constraint containing the conjunct $ \wedge_{\lp \cfgnt{r}^\prime_a,\ \phi^\prime_a,\ l^\prime_a\rp  \in \rho} \cfgnt{r}_f \ne \cfgnt{r}^\prime_a$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{alias}$, because each constraint in that set contains the conjunct $r_f = r_a$ for some $(r_a\ \phi_a\ l_a)\in \rho$. Any two elements of the set $\theta_{alias}$ are guaranteed to pairwise mutually exclusive because for each constraint that contains the conjunct $r_f = r_a$, every other constraint contains the conjunct $r_f \ne r_a$. Thus, all constraints from all pairs in $\theta{all}$ are guaranteed to be mutually exclusive, and the property from Theorem~\ref{thm:mutex} holds for intermediate state $s_\beta$.

We have now shown that whether there are any uninitialized fields or not, the mutual exclusivity property holds for any intermediate state $s_\beta$, so long as $s_\alpha \rightarrow_S s_\beta$ and the property holds for $s_\alpha$. 
So, since the mutual exclusivity property holds for $s_s$, $s_s \rightarrow_S s_1$, and $s_{i} \rightarrow_S s_{i+1} $ for all $i$ such that $0 < i < n$, we are guaranteed that the mutually exclusive property holds for the final intermediate state $s_n$. This concludes the inductive argument about 
\end{comment}
\end{proof}

%\begin{lemma}
%\label{lem:lazyrefprops}
%For any lazy state $s_\ell = ( \cfgnt{L}_\ell\ \cfgnt{R}_\ell\ \phi_\ell\ \eta_\ell\ \cfgnt{e}_\ell\ \cfgnt{k}_\ell )$, for any reference $r \in \cfgnt{L}_\ell^\leftarrow$, 
%$$ | \cfgnt{L}_\ell ( r) | = 1 $$
%\end{lemma}
%
%\begin{proof}
%In every rule in the Lazy machine that establishes a reference mapping, the value set contains exactly one location, constraint pair. 
%\end{proof}

\begin{theorem}[Mutual Exclusion]
\label{thm:mutex}
If we have a reachable summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$
$$ 
\begin{array}{l}
\forall (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_s(\cfgnt{r})\ (\forall (\phi_\beta\ \cfgnt{l}_\beta) \in \cfgnt{L}_s(\cfgnt{r})\ ( \\
\ \ \ \ (\cfgnt{l}_\alpha \neq \cfgnt{l}_\beta) \Rightarrow ((\phi_\alpha \wedge \phi_\beta) = \cfgt{false})))
\end{array}
$$
\end{theorem}
\begin{proof}
The proof will proceed inductively.

@@

We begin by considering the Field Access rule. Suppose $s_s$ has the form $\lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$. In this case, the relationship between $s_s$ and $s_s^\prime$ is described by the Field Access rule. intermediate state.
